Ordinal Tax To Sustain a Digital Economy

### 2019-08-05 writing/short note on digital tax/DigitalTax.tex
added more paper revisions.

Until not too long ago, people used to live in relatively self-contained tribes or villages. 
Trade would exist mostly for specialised products, whereas basic products such as bread or textiles would be produced locally. 
From the industrial to the technological revolution, more efficient distribution channels have emerged, enabling people to buy almost any product in online stores. 
Orders can be delivered often within one or two days, independent of the customer’s physical location. 
Pushing this development to the limit, we arrive at an economy where, at least within country borders, physical distance becomes irrelevant. 
For digital products and services, this is largely reality, and in direct contrast to established economic theories like \cite{Isard1954}'s gravity model of trade, stating that trade activity is inversely proportional to physical distance.

>>>>

Until not too long ago, people used to live in relatively self-contained tribes or villages. 
Basic products such as bread or textiles were produced locally. 
Trade primarily existed for specialised products.  
Over time, from the industrial revolution through present technological advancements, more efficient distribution channels have emerged.
Online orders are often delivered within a couple days, independent of a customer’s physical location. 
Extrapolated, this trend leads to an economy where, at least domestically, physical shipping distance becomes irrelevant. 
For digital products and services, this has largely become a reality and contradicts established economic theories, like \cite{Isard1954}'s gravity model of trade which states that trade activity is inversely proportional to physical distance.
